---
title: "SafeBabies"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---


#Required libraries:

```{r}
library(ISLR)
library(dplyr)
library(ggplot2)
```

#Data segregation:

```{r}
SafeBabies <- Carseats %>% select("Sales", "Price", "ShelveLoc")

head(SafeBabies)

BadSeats <- filter(SafeBabies, ShelveLoc == 'Bad')

GoodSeats <- filter(SafeBabies, ShelveLoc == 'Good')

```

#Model to find b0 & b1 values for the respective two locations:

Why?

Total Profit = Sales * (Price - Production Cost)

Total Profit = (-b1 * Price + b0) * (Price - Production Cost)

By regression we can find values of b0 & b1.

The we can convert Total Profit into a quadratioc equation to find Price by performing derivative of the equation.

```{r}
Model_BadSeats <- lm(Sales ~ Price, data = BadSeats)

Model_GoodSeats <- lm(Sales ~ Price, data = GoodSeats)
```

#Finding Profit by substituting values:

```{r}
Equation_GoodSeats <- expression(-0.065785*P^2 + 17.968864*P*55 + (17.968864)*P +55*0.065785)
Derivative_Price_GoodSeats <- D(Equation_GoodSeats,'P')
Price_GoodSeats <- (-0.065785 *55 - 17.968864)/(2 * -0.065785)
Price_GoodSeats

Equation_BadSeats <- expression(-0.055220*P^2 + 11.832984*P*55 + (11.832984)*P +55*0.055220) 
Derivative_Price_BadSeats <- D(Equation_BadSeats,'P')
Price_BadSeats <- (-0.055220 *55 - 11.832984)/(2 * -0.055220)
Price_BadSeats
```

#Finding for the cost range 40 - 85:

```{r}
c <- 40:85
Optimal_GoodSeats <- numeric(length=length(c))
for (i in seq_along(c)){
   Optimal_GoodSeats[i] <- (-0.065785 *c[i] - 17.968864)/(2 * -0.065785)
}


c <- 40:85
Optimal_BadSeats <- numeric(length=length(c))
for (i in seq_along(c)){
   Optimal_BadSeats[i] <- (-0.055220 *c[i] - 11.832984)/(2 * -0.055220)
}
```

#Plotting:

```{r}

Pricing <- data.frame(Optimal_GoodSeats, Optimal_BadSeats)

ggplot(Pricing) +
geom_smooth(aes(x = c, y = Optimal_GoodSeats, color = "Good"), method = "loess") +
geom_smooth(aes(x = c, y = Optimal_BadSeats, color = "Bad"), method = "loess") +
labs(x = "Production Cost", y = "Optimal Price", title = "Optimal Price vs Production Cost", color = "Shelve Location")
```


